---
title: "Financial Time Series Models(ARCH/GARCH)"
format: html
---

# Finance time series model(KOSPI)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
library(tidyverse)
library(ggplot2)
library(forecast)
library(astsa) 
library(xts)
library(zoo)
library(tseries)
library(fpp2)
library(fma)
library(lubridate)
library(tidyverse)
library(TSstudio)
library(tidyquant)
library(plotly)
library(readr)
library(kableExtra)
library(knitr)
library(patchwork)
library(vars)
library(here)
library(tsibble)
library(dplyr)
# calling data

#KR base rate
bok<- read.csv("../data/interest/bok.csv")%>%
  rename(Date = date)
bok$Date<- as.Date(bok$Date)
bok <- bok %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")


# FED rate 

usr<- read.csv("../data/interest/us_rate.csv")%>%
  rename(Date = observation_date,rate = DFF)
usr$Date<- as.Date(usr$Date)
usr<- usr %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")

# KRW/USD rate

Start_date <- as.Date("1996-12-11")

kr <- read.csv("../data/fx rate/kor.csv")

kr <- kr %>%
  transmute(
    Date = as.Date(observation_date),
    krw  = DEXKOUS,
    usd  = 1 / DEXKOUS
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  # drop any rows before 1996-12-11 (optional but usually desired)
  filter(Date >= Start_date) %>%
  # create a complete daily sequence starting from 1996-12-11
  complete(Date = seq(Start_date, max(Date), by = "day")) %>%
  fill(krw, usd, .direction = "down")


# USD index 

usd <- read_csv("../data/fx rate/usd_index.csv", show_col_types = FALSE)
usd <- usd %>%
  transmute(
    Date = as.Date(Date),
    usd_index = Close
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  complete(Date = seq(min(Date), max(Date), by = "day")) %>%
  fill(usd_index, .direction = "down")


# Yield data 

us_yield  <- read.csv(here("data/yield", "us_yield.csv"))
kor_yield   <- read.csv(here("data/yield", "kor_yield.csv"))


us_yield$Date  <- as.Date(us_yield$Date)
kor_yield$Date <- as.Date(kor_yield$Date)

colnames(us_yield)[colnames(us_yield)  == "X3Y"]  <- "US_3Y"
colnames(us_yield)[colnames(us_yield)  == "X10Y"] <- "US_10Y"
colnames(kor_yield)[colnames(kor_yield) == "X3Y"]  <- "KR_3Y"
colnames(kor_yield)[colnames(kor_yield) == "X10Y"] <- "KR_10Y"

us_yield  <- us_yield[,  c("Date", "US_3Y", "US_10Y")]
kor_yield <- kor_yield[, c("Date", "KR_3Y", "KR_10Y")]

us_yield  <- us_yield  %>% arrange(Date) %>% fill(US_3Y, US_10Y, .direction = "down")
kor_yield <- kor_yield %>% arrange(Date) %>% fill(KR_3Y, KR_10Y, .direction = "down")


df <- merge(us_yield, kor_yield, by = "Date")

df$US_3m10  <- df$US_3Y - df$US_10Y
df$KR_3m10  <- df$KR_3Y - df$KR_10Y
df$US_KR_3Y <- df$US_3Y - df$KR_3Y
df$US_KR_10Y<- df$US_10Y - df$KR_10Y


# S&P500 data
sp500 <- read_csv("../data/stock/sp500.csv")


# KOSPI data
kospi <- read_csv("../data/stock/kospi.csv")
kospi$Date <- as.Date(kospi$Date)

# VIX data(added for the modeling)
vix<- read_csv("../data/stock/vix.csv")%>%
  mutate(Date = ymd(Date)) %>%
  arrange(Date) %>%
  fill(vix, .direction = "down")


# extract spreads from df

us_spreads <- df %>%
  dplyr::select(Date, US_3m10) %>%
  rename(us_spread = US_3m10) %>%
  mutate(Date = as.Date(Date))

kor_spreads <- df %>%
  dplyr::select(Date, KR_3m10) %>%
  rename(kr_spread = KR_3m10) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_3y <- df %>%
  dplyr::select(Date, US_KR_3Y) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_10y <- df %>%
  dplyr::select(Date, US_KR_10Y) %>%
  mutate(Date = as.Date(Date))


```


# Time series plot

::: panel-tabset 


### candelstick plot for KOSPI Index 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

sp_plot <- plot_ly(
  data = kospi,
  x = ~Date,
  type = "candlestick",
  open = ~Open,
  high = ~High,
  low = ~Low,
  close = ~Close,
  name = "KOSPI Index"
) %>%
  layout(
    title = "KOSPI Index",
    yaxis = list(title = "KOSPI index"),
    xaxis = list(
      title = "Date",
      tickformat = "%Y",
      dtick = "M12"
    ),
    legend = list(x = 0.1, y = 0.9)
  )

sp_plot
```

### log return plot of KOSPI return

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_close<- kospi$Close
kospi_ts <- ts(kospi_close,
          start = decimal_date(as.Date("1996-12-11")),
          frequency = 252)

kospi_return<- diff(log(kospi_ts))

autoplot(kospi_return) +
  ggtitle("Daily Log Returns of KOSPI Index") +
  xlab("Time") +
  ylab("Log Return")
```

:::


# ACF & PACF plot

::: panel-tabset


### ACF & PACF plot for log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)
kospi_acf <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf

```

From the plots, KOSPI Index data performs well in terms of autocorrelation by applying log transformation, However there are still some lag points showing autocorrelation. 


### ACF & PACF plot for absolute log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


ggAcf(abs(kospi_return), lag.max = 30) +
  ggtitle("ACF plot of Absolute KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ACF & PACF plot for squared log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ggAcf(kospi_return^2, lag.max = 30) +
  ggtitle("ACF plot of Squared KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ARCH effect test

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

# Load required package
library(FinTS)

# Perform ARCH LM Test on Bitcoin returns
arch_test_result <- ArchTest(kospi_return, lags = 1, demean = TRUE)

# Print results
print(arch_test_result)
```

p-vlaue is smaller than 0.05(default criterion), indicating rejecting null hypothesis, concluding strong evidence for the presence of ARCH(1) effects in the data.

:::

Two plots for applying absolute value and squaring to KOSPI Index shows significant autocorrelation throughout multiple lags, compare to log return. This implies that the returns are not independently and identically distributed, and gives evidence for need to apply conditional variance models such as ARCH or GARCH to capture the underlying time-varying volatility structure.


# Modeling Approach 1: ARIMA +GARCH model

::: panel-tabset

### model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)

kospi_acf <- ggAcf(kospi_ts,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_ts,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log
```

### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ARIMA.c <- function(p_min, p_max, q_min, q_max, data) {
  results <- matrix(NA, nrow = 0, ncol = 6)
  colnames(results) <- c("p", "d", "q", "AIC", "BIC", "AICc")

  for (p in p_min:p_max) {
    for (q in q_min:q_max) {
      for (d in 0:2) {
        if ((p + d + q) <= 12) {  # Complexity constraint
          fit <- Arima(data, order = c(p, d, q))
          metrics <- c(p, d, q, fit$aic, fit$bic, fit$aicc)
          results <- rbind(results, metrics)
        }
      }
    }
  }

  # Convert to data frame
  results_df <- as.data.frame(results)
  colnames(results_df) <- c("p", "d", "q", "AIC", "BIC", "AICc")
  return(results_df)
}

highlight_output = function(output, type="ARIMA") {
    highlight_row <- c(which.min(output$AIC), which.min(output$BIC), which.min(output$AICc))
    knitr::kable(output, align = 'c', caption = paste("Comparison of", type, "Models")) %>%
    kable_styling(full_width = FALSE, position = "center") %>%
    row_spec(highlight_row, bold = TRUE, background = "#FFFF99")  # Highlight row in yellow
}

output <- ARIMA.c(p_min = 0, p_max = 5, q_min = 0, q_max = 5, data = log(kospi_ts))
highlight_output(output)

```

From the table, arima(0,1,1) has lowest BIC and arima(5,1,5) has lowest AIC and AICc

### auto.arima() model

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

auto_model1<-auto.arima(log(kospi_ts))
auto_model1
```


### Model diagnostics 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_data<-log(kospi_ts)
kospi_output1 <- capture.output(sarima(kospi_data, 0, 1, 1))
start_line <- grep("Coefficients", kospi_output1) 
end_line <- length(kospi_output1)  
cat(kospi_output1[start_line:end_line], sep = "\n")
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output2 <- capture.output(sarima(kospi_data, 5, 1, 5))
start_line <- grep("Coefficients", kospi_output2) 
end_line <- length(kospi_output2)  
cat(kospi_output2[start_line:end_line], sep = "\n")

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output3 <- capture.output(sarima(kospi_data, 2, 1, 2))
start_line <- grep("Coefficients", kospi_output3) 
end_line <- length(kospi_output3)  
cat(kospi_output3[start_line:end_line], sep = "\n")
```

From model diagnostic for three potential models, diagnostics are not satisfactory, to evaluate which model to choose, model AIC,BIC and coefficient's significance. In this sense, i would use ARIMA(0,1,1) model since it has lowest BIC value. 


:::


# residual fit


::: panel-tabset

### Residual ACF &PACF plot of KOSPI Index model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf

```

### Squared Residual ACF &PACF plot of KOSPI Index model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1^2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1^2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf
```



### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(tseries)
library(knitr)
library(kableExtra)

# Initialize list to store models and track p, q
models <- list()
pq_combinations <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Fit GARCH(p, q) models for p = 1:7 and q = 1:7
for (p in 0:5) {
  for (q in 0:5) {
    fit <- tryCatch(
      garch(res_arima1, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      pq_combinations <- rbind(
        pq_combinations,
        data.frame(p = p, q = q, AIC = AIC(fit))
      )
      cc <- cc + 1
    }
  }
}

# Round AIC for presentation
pq_combinations$AIC <- round(pq_combinations$AIC, 3)

# Identify row with minimum AIC
highlight_row <- which.min(pq_combinations$AIC)

# Create formatted table
pq_combinations %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(2,3):\n")
garch_model <- garchFit(~ garch(2, 3), data = res_arima1, trace = FALSE)
summary(garch_model)
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
cat("\nSummary for GARCH(2,1):\n")
garch_model <- garchFit(~ garch(2, 1), data = res_arima1, trace = FALSE)
summary(garch_model)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(1,1):\n")
garch_model <- garchFit(~ garch(1,1), data = res_arima1, trace = FALSE)
summary(garch_model)
```
By manual search to find optimal p,q value, GARCH(2,3) had lowest AIC. However when fitting a model with this parameter, beta 1 and beta 2 are not significant with large p value, trying other close by AIC values could be appropriate. After testing two more models, all the coefficient for GARCH(1,1) model are significant and very close AIC value to lowest value, So further modeling GARCH(1,1) will be used. 

### Final model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
#| 
arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
arima_res1<-residuals(arima_fit1)
final.fit1<- garchFit(~ garch(1, 1), data = arima_res1, trace = FALSE)
summary(final.fit1)
```
### forecasting
```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

fc <-predict(final.fit1, n.ahead = 100)
invisible(predict(final.fit1, n.ahead = 100, plot = TRUE))
```

:::


# Modeling Approach 2: GARCH model

::: panel-tabset

### ACF & PACF plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log

```

### Manual Search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


# Initialize model storage
models <- list()
results <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Grid search for GARCH(p, q), where p = ARCH order, q = GARCH order
for (p in 1:5) {
  for (q in 1:5) {
    fit <- tryCatch(
      garch(kospi_return, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      results <- rbind(results, data.frame(p = p, q = q, AIC = AIC(fit)))
      cc <- cc + 1
    }
  }
}

# Round AIC values for readability
results$AIC <- round(results$AIC, 3)

# Identify the model with the lowest AIC
highlight_row <- which.min(results$AIC)

# Display formatted table
results %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")

```


### Model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model1 <- garchFit(~ garch(4,3), data = kospi_return, trace = FALSE)
summary(garch_model1)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model2 <- garchFit(~ garch(2,1), data = kospi_return, trace = FALSE)
summary(garch_model2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model3 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
summary(garch_model3)
```

### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


garch.fit2 <- garch(kospi_return, order = c(1,1), trace = FALSE) 
summary(garch.fit2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_res1 <- residuals(garch.fit2)
checkresiduals(garch_res1)
```

:::

# Forecast & Volatility 

::: panel-tabset 

### Forecasting plot(365 days)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


library(fGarch)
library(lubridate)
library(dplyr)
library(plotly)


gfit <- garchFit(~ garch(1,1),
                 data = as.numeric(kospi_return),
                 trace = FALSE)

h <- 365
pf <- predict(gfit, n.ahead = h)
rhat <- as.numeric(pf$meanForecast)


last_price <- tail(as.numeric(kospi_close), 1)
price_fc <- numeric(h)
price_fc[1] <- last_price * exp(rhat[1])
for (i in 2:h) {
  price_fc[i] <- price_fc[i-1] * exp(rhat[i])
}

last_date <- tail(kospi$Date, 1) 
future_dates <- seq(last_date + 1, by = "day", length.out = h)

hist_df <- data.frame(
  Date = kospi$Date,  
  Price = as.numeric(kospi_close)
)

fc_df <- data.frame(Date = future_dates, Price = price_fc)

recent_window <- 3650 # recent 10 years
hist_df_recent <- tail(hist_df, recent_window)

plot_ly() %>%
  add_lines(data = hist_df_recent, x = ~Date, y = ~Price, 
            name = "Historical", line = list(color="blue")) %>%
  add_lines(data = fc_df, x = ~Date, y = ~Price, 
            name = "GARCH Forecast", 
            line = list(color="red", dash="dash")) %>%
  layout(title = "KOSPI — GARCH(1,1) 365-Day Price Forecast",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Index"),
         hovermode = "x unified")
```


### Volatility plot 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
set.seed(1)

garch.fit11 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
ht <- garch.fit11@h.t


data2 <- data.frame(Date = kospi$Date[-1][1:length(ht)], Volatility = ht)



p <- ggplot(data2, aes(x = Date, y = Volatility)) +
  geom_line(color = 'orange') +
  labs(
    title = "Conditional Variance from GARCH(1,1) Model",
    x = "Date",
    y = "Conditional Variance"
  ) +
  theme_minimal()

# Convert to plotly
ggplotly(p)
```

:::


# Financial time series moodel(KRW/USD spot rate)

::: panel-tabset 

### time series plot for KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

p_us <- plot_ly(kr, x = ~Date, y = ~krw, type = "scatter", mode = "lines",
                 name = "USD per KRW") %>%
  layout(title = "USD per KRW",
         xaxis = list(title = "Date"),
         yaxis = list(title = "USD per KRW"))
p_us
```

### reutrn of KRW/USD exchange spot plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_ts <- ts(kr$krw,
          start = decimal_date(as.Date("1996-12-11")),
          frequency = 252)

#kr_return<- diff(kr_ts)
kr_return <- diff(kr_ts) / kr_ts[-length(kr_ts)]
autoplot(kr_return) +
  ggtitle("Daily Returns of KRW/USD exchange spot") +
  xlab("Time") +
  ylab("Log Return")
```

:::


# ACF & PACF plot

::: panel-tabset


### ACF & PACF plot for  return of KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)
kr_acf <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf/kr_pacf

```

From the plots, KOSPI Index data performs well in terms of autocorrelation by applying log transformation, However there are still some lag points showing autocorrelation. 


### ACF & PACF plot for  return of KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


ggAcf(abs(kr_return), lag.max = 30) +
  ggtitle("ACF plot of Absolute 
          KRW/USD exchange spot") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ACF & PACF plot for return of KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ggAcf(kr_return^2, lag.max = 30) +
  ggtitle("ACF plot of Squared
          KRW/USD exchange spot ") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```


### ARCH effect test

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

# Load required package
library(FinTS)

# Perform ARCH LM Test on Bitcoin returns
arch_test_result <- ArchTest(kr_return, lags = 1, demean = TRUE)

# Print results
print(arch_test_result)
```

p-vlaue is smaller than 0.05(default criterion), indicating rejecting null hypothesis, concluding strong evidence for the presence of ARCH(1) effects in the data.


:::

Two plots for applying absolute value and squaring to KOSPI Index shows significant autocorrelation throughout multiple lags, compare to log return. This implies that the returns are not independently and identically distributed, and gives evidence for need to apply conditional variance models such as ARCH or GARCH to capture the underlying time-varying volatility structure.


# Modeling 1: ARIMA +GARCH model

::: panel-tabset

### model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)

kr_acf <- ggAcf(kr_ts,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot ") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf <- ggPacf(kr_ts,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf/kr_pacf
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_acf_log <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf_log <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf_log/kr_pacf_log
```

### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ARIMA.c <- function(p_min, p_max, q_min, q_max, data) {
  results <- matrix(NA, nrow = 0, ncol = 6)
  colnames(results) <- c("p", "d", "q", "AIC", "BIC", "AICc")

  for (p in p_min:p_max) {
    for (q in q_min:q_max) {
      for (d in 0:2) {
        if ((p + d + q) <= 12) {  # Complexity constraint
          fit <- Arima(data, order = c(p, d, q))
          metrics <- c(p, d, q, fit$aic, fit$bic, fit$aicc)
          results <- rbind(results, metrics)
        }
      }
    }
  }

  # Convert to data frame
  results_df <- as.data.frame(results)
  colnames(results_df) <- c("p", "d", "q", "AIC", "BIC", "AICc")
  return(results_df)
}

highlight_output = function(output, type="ARIMA") {
    highlight_row <- c(which.min(output$AIC), which.min(output$BIC), which.min(output$AICc))
    knitr::kable(output, align = 'c', caption = paste("Comparison of", type, "Models")) %>%
    kable_styling(full_width = FALSE, position = "center") %>%
    row_spec(highlight_row, bold = TRUE, background = "#FFFF99")  # Highlight row in yellow
}

output <- ARIMA.c(p_min = 0, p_max = 4, q_min = 0, q_max = 4, data = kr_ts)
highlight_output(output)

```

From the table, arima(0,1,1) has lowest BIC and arima(5,1,5) has lowest AIC and AICc

### auto.arima() model

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

auto_model2<-auto.arima(kr_ts)
auto_model2
```

### Model diagnostics 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_data<- kr_ts
kr_output1 <- capture.output(sarima(kr_data, 4, 1, 4))
start_line <- grep("Coefficients", kr_output1) 
end_line <- length(kr_output1)  
cat(kr_output1[start_line:end_line], sep = "\n")
```


From model diagnostic for three potential models, diagnostics are not satisfactory, to evaluate which model to choose, model AIC,BIC and coefficient's significance. In this sense, i would use ARIMA(4,1,4) model since it has lowest BIC value. Also auto.arima() suggested ARIMA(0,1,0)(0,0,1)[252], however as seen in EDA and univariate section, using ARIMA(4,1,4) is more appropriate. 


:::


# Residual fit

::: panel-tabset

### Residual ACF &PACF plot for KRW/USD exchange spot model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


arima_fit2 <- Arima(kr_ts, order = c(4,1,4), include.drift = TRUE)
res_arima2<- residuals(arima_fit2)

kr_res_acf <- ggAcf(res_arima2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_pacf <- ggPacf(res_arima2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_acf/kr_res_pacf

```


### Squared Residual ACF &PACF plot for KRW/USD exchange spot model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_res_acf <- ggAcf(res_arima2^2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_pacf <- ggPacf(res_arima2^2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_acf/kr_res_pacf
```


### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(tseries)
library(knitr)
library(kableExtra)

# Initialize list to store models and track p, q
models <- list()
pq_combinations <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

for (p in 0:4) {
  for (q in 0:4) {
    fit <- tryCatch(
      garch(res_arima2, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      pq_combinations <- rbind(
        pq_combinations,
        data.frame(p = p, q = q, AIC = AIC(fit))
      )
      cc <- cc + 1
    }
  }
}

# Round AIC for presentation
pq_combinations$AIC <- round(pq_combinations$AIC, 3)

# Identify row with minimum AIC
highlight_row <- which.min(pq_combinations$AIC)

# Create formatted table
pq_combinations %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")
```

### Model selection 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(2,1):\n")
garch_model <- garchFit(~ garch(2, 1), data = res_arima2, trace = FALSE)
summary(garch_model)
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(1,1):\n")
garch_model <- garchFit(~ garch(1,1), data = res_arima2, trace = FALSE)
summary(garch_model)
```

By manual search to find optimal p,q value, GARCH(2,1) had lowest AIC. However when fitting a model with this parameter, alpha2 are not significant with large p value, trying other close by AIC values could be appropriate. After testing more model, all the coefficient for GARCH(1,1) model are significant and very close AIC value to lowest value, So further modeling GARCH(1,1) will be used. 

### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
#| 
arima_fit2 <- Arima(kr_ts, order = c(4,1,4), include.drift = TRUE)
arima_res2<-residuals(arima_fit2)
final.fit2<- garchFit(~ garch(1, 1), data = arima_res2, trace = FALSE)
summary(final.fit2)
```

### Forecast


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

fc <-predict(final.fit2, n.ahead = 100)
invisible(predict(final.fit2, n.ahead = 100, plot = TRUE))
```

:::


# Modeling Approach 2: GARCH model

::: panel-tabset

### ACF & PACF plot of KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_acf_log <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf_log <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf_log/kr_pacf_log

```

### Manual Search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


# Initialize model storage
models <- list()
results <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Grid search for GARCH(p, q), where p = ARCH order, q = GARCH order
for (p in 1:5) {
  for (q in 1:5) {
    fit <- tryCatch(
      garch(kr_return, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      results <- rbind(results, data.frame(p = p, q = q, AIC = AIC(fit)))
      cc <- cc + 1
    }
  }
}

# Round AIC values for readability
results$AIC <- round(results$AIC, 3)

# Identify the model with the lowest AIC
highlight_row <- which.min(results$AIC)

# Display formatted table
results %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")

```


### Model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model2 <- garchFit(~ garch(1,3), data = kr_return, trace = FALSE)
summary(garch_model2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model3 <- garchFit(~ garch(1,1), data = kr_return, trace = FALSE)
summary(garch_model3)
```

### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


garch.fit2 <- garch(kr_return, order = c(1,1), trace = FALSE) 
summary(garch.fit2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_res2 <- residuals(garch.fit2)
checkresiduals(garch_res2)
```

:::

# Forecast & Volatility

::: panel-tabset

### Forecasting plot(365days)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
library(lubridate)
library(dplyr)
library(plotly)


gfit <- garchFit(~ garch(1,1),
                 data = as.numeric(kr_return),
                 trace = FALSE)

# Forecast 365 days
h <- 365
pf <- predict(gfit, n.ahead = h)
rhat <- as.numeric(pf$meanForecast)

# Convert differences to prices (simple addition)
last_price <- tail(as.numeric(kr$krw), 1)
price_fc <- numeric(h)
price_fc[1] <- last_price + rhat[1]
for (i in 2:h) {
  price_fc[i] <- price_fc[i-1] + rhat[i]
}

# Create future dates
last_date <- tail(kr$Date, 1) 
future_dates <- seq(last_date + 1, by = "day", length.out = h)

# Historical data
hist_df <- data.frame(
  Date = kr$Date,  
  Price = as.numeric(kr$krw)
)

# Forecast data
fc_df <- data.frame(Date = future_dates, Price = price_fc)

# Show recent 10 years
recent_window <- 3650
hist_df_recent <- tail(hist_df, recent_window)

# Plot
plot_ly() %>%
  add_lines(data = hist_df_recent, x = ~Date, y = ~Price, 
            name = "Historical", line = list(color="blue", width=2)) %>%
  add_lines(data = fc_df, x = ~Date, y = ~Price, 
            name = "GARCH Forecast", 
            line = list(color="red", dash="dash", width=3)) %>%
  layout(title = "KRW/USD Exchange Rate — GARCH(1,1) 365-Day Forecast",
         xaxis = list(title = "Date"),
         yaxis = list(title = "KRW per USD"),
         hovermode = "x unified")
```

### Volatility plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
set.seed(1)


garch.fit11 <- garchFit(~ garch(1,1), data = kr_return, trace = FALSE)
ht <- garch.fit11@h.t


data2 <- data.frame(Date = kr$Date[-1][1:length(ht)], Volatility = ht)



p <- ggplot(data2, aes(x = Date, y = Volatility)) +
  geom_line(color = 'orange') +
  labs(
    title = "Conditional Variance from GARCH(1,1) Model",
    x = "Date",
    y = "Conditional Variance"
  ) +
  theme_minimal()
ggplotly(p)
```

:::








