---
title: "Financial Time Series Models(ARCH/GARCH)"
format: html
---

# Introduction

The focus of this section is on building financial time series models, specifically for the KOSPI Index and the KRW/USD spot exchange rate. The aim of this project is to examine the influence of the United States on the South Korean economy. More specifically, in this section the goal is to examine how dollar exchange rate risk affects the Korean economy.

The KOSPI Index serves as the main equity index for the Korean financial market and visibly reflects the overall state of Korea’s economy. The exchange rate is a very unique financial asset: it behaves like an equity asset, but is also closely related to the policy rate. Because the exchange rate reflects the value of a currency, governments use it as one of the indicators when deciding their policy rate. Since one variable (the KOSPI) reflects the pure market condition and the other (the exchange rate) contains information about currency value and monetary policy, together they form a strong set of indicators for this project.

The previous section (on multivariate time series models) focused on interactions among variables and their effects. This section instead focuses on the volatility of the variables. As financial assets, the KOSPI Index and the exchange rate are heavily influenced by various factors, which leads to volatility clustering: periods of high volatility tend to be followed by similarly turbulent periods, while calm periods also cluster together. In other words, volatility changes over time depending on past shocks and past variance. Therefore, the focus of this section is to examine volatility and its patterns by applying ARCH/GARCH models.
Using these models, the aim is to understand how the volatility of the KOSPI Index and the KRW/USD exchange rate has evolved over time and how major economic crises have affected them. From this analysis, it will be possible to gain deeper intuition about how the value of the Korean won against the U.S. dollar impacts the Korean economy, particularly from a risk management perspective. For further research, the aim is to derive implications for constructing investment portfolios for effective risk management.


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
library(tidyverse)
library(ggplot2)
library(forecast)
library(astsa) 
library(xts)
library(zoo)
library(tseries)
library(fpp2)
library(fma)
library(lubridate)
library(tidyverse)
library(TSstudio)
library(tidyquant)
library(plotly)
library(readr)
library(kableExtra)
library(knitr)
library(patchwork)
library(vars)
library(here)
library(tsibble)
library(dplyr)
# calling data

#KR base rate
bok<- read.csv("../data/interest/bok.csv")%>%
  rename(Date = date)
bok$Date<- as.Date(bok$Date)
bok <- bok %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")


# FED rate 

usr<- read.csv("../data/interest/us_rate.csv")%>%
  rename(Date = observation_date,rate = DFF)
usr$Date<- as.Date(usr$Date)
usr<- usr %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")

# KRW/USD rate

Start_date <- as.Date("1996-12-11")

kr <- read.csv("../data/fx rate/kor.csv")

kr <- kr %>%
  transmute(
    Date = as.Date(observation_date),
    krw  = DEXKOUS,
    usd  = 1 / DEXKOUS
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  # drop any rows before 1996-12-11 (optional but usually desired)
  filter(Date >= Start_date) %>%
  # create a complete daily sequence starting from 1996-12-11
  complete(Date = seq(Start_date, max(Date), by = "day")) %>%
  fill(krw, usd, .direction = "down")


# USD index 

usd <- read_csv("../data/fx rate/usd_index.csv", show_col_types = FALSE)
usd <- usd %>%
  transmute(
    Date = as.Date(Date),
    usd_index = Close
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  complete(Date = seq(min(Date), max(Date), by = "day")) %>%
  fill(usd_index, .direction = "down")


# Yield data 

us_yield  <- read.csv(here("data/yield", "us_yield.csv"))
kor_yield   <- read.csv(here("data/yield", "kor_yield.csv"))


us_yield$Date  <- as.Date(us_yield$Date)
kor_yield$Date <- as.Date(kor_yield$Date)

colnames(us_yield)[colnames(us_yield)  == "X3Y"]  <- "US_3Y"
colnames(us_yield)[colnames(us_yield)  == "X10Y"] <- "US_10Y"
colnames(kor_yield)[colnames(kor_yield) == "X3Y"]  <- "KR_3Y"
colnames(kor_yield)[colnames(kor_yield) == "X10Y"] <- "KR_10Y"

us_yield  <- us_yield[,  c("Date", "US_3Y", "US_10Y")]
kor_yield <- kor_yield[, c("Date", "KR_3Y", "KR_10Y")]

us_yield  <- us_yield  %>% arrange(Date) %>% fill(US_3Y, US_10Y, .direction = "down")
kor_yield <- kor_yield %>% arrange(Date) %>% fill(KR_3Y, KR_10Y, .direction = "down")


df <- merge(us_yield, kor_yield, by = "Date")

df$US_3m10  <- df$US_3Y - df$US_10Y
df$KR_3m10  <- df$KR_3Y - df$KR_10Y
df$US_KR_3Y <- df$US_3Y - df$KR_3Y
df$US_KR_10Y<- df$US_10Y - df$KR_10Y


# S&P500 data
sp500 <- read_csv("../data/stock/sp500.csv")


# KOSPI data
kospi <- read_csv("../data/stock/kospi.csv")
kospi$Date <- as.Date(kospi$Date)

# VIX data(added for the modeling)
vix<- read_csv("../data/stock/vix.csv")%>%
  mutate(Date = ymd(Date)) %>%
  arrange(Date) %>%
  fill(vix, .direction = "down")


# extract spreads from df

us_spreads <- df %>%
  dplyr::select(Date, US_3m10) %>%
  rename(us_spread = US_3m10) %>%
  mutate(Date = as.Date(Date))

kor_spreads <- df %>%
  dplyr::select(Date, KR_3m10) %>%
  rename(kr_spread = KR_3m10) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_3y <- df %>%
  dplyr::select(Date, US_KR_3Y) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_10y <- df %>%
  dplyr::select(Date, US_KR_10Y) %>%
  mutate(Date = as.Date(Date))


```


# Finance time series model(KOSPI)

## Time series plot

::: panel-tabset 


### candelstick plot for KOSPI Index 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

sp_plot <- plot_ly(
  data = kospi,
  x = ~Date,
  type = "candlestick",
  open = ~Open,
  high = ~High,
  low = ~Low,
  close = ~Close,
  name = "KOSPI Index"
) %>%
  layout(
    title = "KOSPI Index",
    yaxis = list(title = "KOSPI index"),
    xaxis = list(
      title = "Date",
      tickformat = "%Y",
      dtick = "M12"
    ),
    legend = list(x = 0.1, y = 0.9)
  )

sp_plot
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

gg <- ggplot(kospi, aes(x = Date, y = log(Close))) +   
  geom_line(color = 'skyblue') +  
  labs(x = "Year", title = "KOSPI Index(Log transformed)")

plotly_gg <- ggplotly(gg)
plotly_gg
```

### log return plot of KOSPI return

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_close<- kospi$Close
kospi_ts <- ts(kospi_close,
          start = decimal_date(as.Date("1996-12-11")),
          frequency = 252)

kospi_return<- diff(log(kospi_ts))

autoplot(kospi_return) +
  ggtitle("Daily Log Returns of KOSPI Index") +
  xlab("Time") +
  ylab("Log Return")
```

:::

As discussed in the univariate and multivariate time series model sections, the log transformation performed well for the KOSPI data, so it was applied to the KOSPI closing prices. The first plot is a candlestick chart of the KOSPI Index, and the second is the log-transformed KOSPI data. It is evident that applying the log transformation reduces variability.

The third plot shows the log returns of the KOSPI Index. In this plot, volatility clustering is clearly observed: for most periods, the values are centered near zero, but in certain periods the series exhibits high volatility before returning to calmer behavior. This suggests that the data are potentially appropriate for modeling with the ARCH/GARCH family of models.



# ACF & PACF plot

::: panel-tabset


### ACF & PACF plot for log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)
kospi_acf <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf

```

From the plots, KOSPI Index data performs well in terms of autocorrelation by applying log transformation, However there are still some lag points showing autocorrelation. 


### ACF & PACF plot for absolute log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


ggAcf(abs(kospi_return), lag.max = 30) +
  ggtitle("ACF plot of Absolute KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ACF & PACF plot for squared log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ggAcf(kospi_return^2, lag.max = 30) +
  ggtitle("ACF plot of Squared KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ARCH effect test

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

# Load required package
library(FinTS)

# Perform ARCH LM Test on Bitcoin returns
arch_test_result <- ArchTest(kospi_return, lags = 1, demean = TRUE)

# Print results
print(arch_test_result)
```

p-vlaue is smaller than 0.05(default criterion), indicating rejecting null hypothesis, concluding strong evidence for the presence of ARCH(1) effects in the data.

:::

Two plots for applying absolute value and squaring to KOSPI Index shows significant autocorrelation throughout multiple lags, compare to log return. This implies that the returns are not independently and identically distributed, and gives evidence for need to apply conditional variance models such as ARCH or GARCH to capture the underlying time-varying volatility structure.


# Modeling Approach 1: ARIMA +GARCH model

::: panel-tabset

### model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)

kospi_acf <- ggAcf(kospi_ts,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_ts,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index return") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index return") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log
```

The ACF plot shows significant autocorrelation across several lags. In the PACF plot, there is a strong autocorrelation at lag 1, followed by a sharp drop, indicating almost no autocorrelation after lag 1. These plots suggest the presence of dependencies between past and current price movements, and that the series is stationary.

For the KOSPI index returns, the ACF and PACF plots show that most lags lie within the significance bounds; however, there are a few spikes at certain lags, such as lag 5. For manual model selection, a search range from 0 to 5 therefore seems appropriate.

Both plots exhibit similar patterns, indicating that conditional heteroskedasticity is present in the return series. Thus, applying models from the ARCH/GARCH family is appropriate.


### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ARIMA.c <- function(p_min, p_max, q_min, q_max, data) {
  results <- matrix(NA, nrow = 0, ncol = 6)
  colnames(results) <- c("p", "d", "q", "AIC", "BIC", "AICc")

  for (p in p_min:p_max) {
    for (q in q_min:q_max) {
      for (d in 0:2) {
        if ((p + d + q) <= 12) {  # Complexity constraint
          fit <- Arima(data, order = c(p, d, q))
          metrics <- c(p, d, q, fit$aic, fit$bic, fit$aicc)
          results <- rbind(results, metrics)
        }
      }
    }
  }

  # Convert to data frame
  results_df <- as.data.frame(results)
  colnames(results_df) <- c("p", "d", "q", "AIC", "BIC", "AICc")
  return(results_df)
}

highlight_output = function(output, type="ARIMA") {
    highlight_row <- c(which.min(output$AIC), which.min(output$BIC), which.min(output$AICc))
    knitr::kable(output, align = 'c', caption = paste("Comparison of", type, "Models")) %>%
    kable_styling(full_width = FALSE, position = "center") %>%
    row_spec(highlight_row, bold = TRUE, background = "#FFFF99")  # Highlight row in yellow
}

output <- ARIMA.c(p_min = 0, p_max = 5, q_min = 0, q_max = 5, data = log(kospi_ts))
highlight_output(output)

```

From the table, arima(0,1,1) has lowest BIC and arima(5,1,5) has lowest AIC and AICc

### auto.arima() model

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

auto_model1<-auto.arima(log(kospi_ts))
auto_model1
```

auto.arima() suggest ARIMA(2,1,2) model

### Model diagnostics 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_data<-log(kospi_ts)
kospi_output1 <- capture.output(sarima(kospi_data, 0, 1, 1))
start_line <- grep("Coefficients", kospi_output1) 
end_line <- length(kospi_output1)  
cat(kospi_output1[start_line:end_line], sep = "\n")
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output2 <- capture.output(sarima(kospi_data, 5, 1, 5))
start_line <- grep("Coefficients", kospi_output2) 
end_line <- length(kospi_output2)  
cat(kospi_output2[start_line:end_line], sep = "\n")

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output3 <- capture.output(sarima(kospi_data, 2, 1, 2))
start_line <- grep("Coefficients", kospi_output3) 
end_line <- length(kospi_output3)  
cat(kospi_output3[start_line:end_line], sep = "\n")
```

Three models were tested: ARIMA(0,1,1), ARIMA(5,1,5), and ARIMA(2,1,2).

From the model diagnostics for these three candidates, the results are not fully satisfactory. Therefore, to decide which model to use, I compare their AIC and BIC values as well as the significance of the coefficients. Based on these criteria, I choose the ARIMA(0,1,1) model, since it has the lowest BIC value.

:::


# residual fit


::: panel-tabset

### Residual ACF & PACF plot and Squared Residual ACF &PACF plot of KOSPI Index model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1^2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1^2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf
```


From the ACF and PACF plots of the residuals and squared residuals for the ARIMA(0,1,1) model, the ACF of the squared residuals shows noticeable spikes up to lag 5, followed by a gradual decline. This suggests the presence of an ARCH effect, indicating time-varying volatility in the data. Based on these plots, an appropriate range for manual model search is p,q both in 0:5 range.


### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(tseries)
library(knitr)
library(kableExtra)

# Initialize list to store models and track p, q
models <- list()
pq_combinations <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Fit GARCH(p, q) models for p = 1:7 and q = 1:7
for (p in 0:5) {
  for (q in 0:5) {
    fit <- tryCatch(
      garch(res_arima1, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      pq_combinations <- rbind(
        pq_combinations,
        data.frame(p = p, q = q, AIC = AIC(fit))
      )
      cc <- cc + 1
    }
  }
}

# Round AIC for presentation
pq_combinations$AIC <- round(pq_combinations$AIC, 3)

# Identify row with minimum AIC
highlight_row <- which.min(pq_combinations$AIC)

# Create formatted table
pq_combinations %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(2,3):\n")
garch_model <- garchFit(~ garch(2, 3), data = res_arima1, trace = FALSE)
summary(garch_model)
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
cat("\nSummary for GARCH(2,1):\n")
garch_model <- garchFit(~ garch(2, 1), data = res_arima1, trace = FALSE)
summary(garch_model)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(1,1):\n")
garch_model <- garchFit(~ garch(1,1), data = res_arima1, trace = FALSE)
summary(garch_model)
```

By manually searching over possible p,qp, qp,q values, the GARCH(2,3) model was found to have the lowest AIC. However, when fitting this model, beta1 and beta2​ were not statistically significant, with large p-values, suggesting that trying models with slightly higher AIC values could be appropriate. After testing two additional models, all coefficients in the GARCH(1,1) model were found to be significant, and its AIC was very close to the minimum observed. Therefore, the GARCH(1,1) model is selected for further analysis.


### Final model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
#| 
arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
arima_res1<-residuals(arima_fit1)
final.fit1<- garchFit(~ garch(1,1), data = arima_res1, trace = FALSE)
summary(final.fit1)
garch_res1 <- residuals(final.fit1)
checkresiduals(garch_res1)

```

### forecasting
```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

fc <-predict(final.fit1, n.ahead = 100)
invisible(predict(final.fit1, n.ahead = 100, plot = TRUE))
```


:::

For the final model, an ARIMA(0,1,1) + GARCH(1,1) specification was used. The model diagnostics provide some insight into its performance. The residual plot shows a reasonably good pattern, with no obvious systematic structure and only a few noticeable spikes. The ACF plot of the residuals indicates that most lags fall within the significance bounds, suggesting that autocorrelation has been largely resolved.

However, the Ljung–Box test yields a very small p-value (0.007), indicating that the model fit is not fully satisfactory and that some dependence may remain in the residuals. Even so, this model is preferred because all of its coefficients are statistically significant, unlike the alternative specifications considered. Therefore, this is taken as the best model among the candidates.

Equation: 

$$
\phi(B) x_t = \delta + \theta(B) y_t,
$$

where

$$
\phi(B) = 1 - B, \qquad
\theta(B) = 1 + \theta_1 B,
$$

$$
y_t = \sigma_t \varepsilon_t, \qquad \varepsilon_t \sim \text{i.i.d. } N(0,1),
$$


$$
\operatorname{var}(y_t \mid y_{t-1}) = \sigma_t^2 
= \alpha_0 + \alpha_1 y_{t-1}^2 + \beta_1 \sigma_{t-1}^2.
$$

$$
\Delta x_t = 0.0002 + y_t + 0.0571\,y_{t-1},
$$

$$
\sigma_t^2 = 1.3026\times 10^{-6}
+ 0.086232\,y_{t-1}^2
+ 0.91126\,\sigma_{t-1}^2.
$$


# Modeling Approach 2: GARCH model

In the previous modeling, the overall model fit was not satisfactory. Therefore, in this section, a different modeling approach is used: directly applying models from the ARCH/GARCH family.

::: panel-tabset

### ACF & PACF plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log

```

Based on the ACF and PACF plots, the parameter search range for the manual selection process will be set from 0 to 5 for both p and q.

### Manual Search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


# Initialize model storage
models <- list()
results <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Grid search for GARCH(p, q), where p = ARCH order, q = GARCH order
for (p in 1:5) {
  for (q in 1:5) {
    fit <- tryCatch(
      garch(kospi_return, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      results <- rbind(results, data.frame(p = p, q = q, AIC = AIC(fit)))
      cc <- cc + 1
    }
  }
}

# Round AIC values for readability
results$AIC <- round(results$AIC, 3)

# Identify the model with the lowest AIC
highlight_row <- which.min(results$AIC)

# Display formatted table
results %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")

```

Optimal model based on AIC is GARCH(4,2) model.

### Model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model1 <- garchFit(~ garch(4,2), data = kospi_return, trace = FALSE)
summary(garch_model1)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model2 <- garchFit(~ garch(2,1), data = kospi_return, trace = FALSE)
summary(garch_model2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model3 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
summary(garch_model3)
```

When testing the model with the lowest AIC, the overall fit was strong; however, not all coefficients were statistically significant, with some showing large p-values. Therefore, two additional models were considered: one with an AIC value close to the minimum and another specified as GARCH(1,1).Comparing the three models, all coefficients in the GARCH(1,1) model were significant, so this model is selected as the final choice.


### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


garch.fit2 <- garch(kospi_return, order = c(1,1), trace = FALSE) 
summary(garch.fit2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_res1 <- residuals(garch.fit2)
checkresiduals(garch_res1)
```

From model diagnostics, this model shows similar result for ACF and residual plot compare to other model approach. However, for Ljung-Box test, it has much better p-value, indicating that this model has better model fit compare to other method. 

:::

Equation: 


$$
r_t = \sigma_t \varepsilon_t, \qquad \varepsilon_t \sim \text{i.i.d. } N(0,1),
$$

$$
\sigma_t^2 = \alpha_0 + \alpha_1 r_{t-1}^2 + \beta_1 \sigma_{t-1}^2.
$$

$$
\alpha_0 = 1.278\times 10^{-6}, \quad
\alpha_1 = 0.08535, \quad
\beta_1 = 0.9123,
$$


$$
\sigma_t^2
= 1.278\times 10^{-6}
+ 0.08535\, r_{t-1}^2
+ 0.9123\, \sigma_{t-1}^2.
$$

# Forecasting plot(365 days) : KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


library(fGarch)
library(lubridate)
library(dplyr)
library(plotly)


gfit <- garchFit(~ garch(1,1),
                 data = as.numeric(kospi_return),
                 trace = FALSE)

h <- 365
pf <- predict(gfit, n.ahead = h)
rhat <- as.numeric(pf$meanForecast)


last_price <- tail(as.numeric(kospi_close), 1)
price_fc <- numeric(h)
price_fc[1] <- last_price * exp(rhat[1])
for (i in 2:h) {
  price_fc[i] <- price_fc[i-1] * exp(rhat[i])
}

last_date <- tail(kospi$Date, 1) 
future_dates <- seq(last_date + 1, by = "day", length.out = h)

hist_df <- data.frame(
  Date = kospi$Date,  
  Price = as.numeric(kospi_close)
)

fc_df <- data.frame(Date = future_dates, Price = price_fc)

recent_window <- 3650 # recent 10 years
hist_df_recent <- tail(hist_df, recent_window)

plot_ly() %>%
  add_lines(data = hist_df_recent, x = ~Date, y = ~Price, 
            name = "Historical", line = list(color="blue")) %>%
  add_lines(data = fc_df, x = ~Date, y = ~Price, 
            name = "GARCH Forecast", 
            line = list(color="red", dash="dash")) %>%
  layout(title = "KOSPI — GARCH(1,1) 365-Day Price Forecast",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Index"),
         hovermode = "x unified")
```


# Volatility plot : KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
set.seed(1)

garch.fit11 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
ht <- garch.fit11@h.t


data2 <- data.frame(Date = kospi$Date[-1][1:length(ht)], Volatility = ht)



p <- ggplot(data2, aes(x = Date, y = Volatility)) +
  geom_line(color = 'orange') +
  labs(
    title = "Conditional Variance from GARCH(1,1) Model",
    x = "Date",
    y = "Conditional Variance"
  ) +
  theme_minimal()

ggplotly(p)
```

:::


# Financial time series moodel(KRW/USD spot rate)

::: panel-tabset 

### time series plot for KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

p_us <- plot_ly(kr, x = ~Date, y = ~krw, type = "scatter", mode = "lines",
                 name = "USD per KRW") %>%
  layout(title = "USD per KRW",
         xaxis = list(title = "Date"),
         yaxis = list(title = "USD per KRW"))
p_us
```

### reutrn of KRW/USD exchange spot plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_ts <- ts(kr$krw,
          start = decimal_date(as.Date("1996-12-11")),
          frequency = 252)

#kr_return<- diff(kr_ts)
kr_return <- diff(kr_ts) / kr_ts[-length(kr_ts)]
autoplot(kr_return) +
  ggtitle("Daily Returns of KRW/USD exchange spot") +
  xlab("Time") +
  ylab("Log Return")
```

:::

As discussed in the univariate and multivariate time series model sections, for exchange rate data,log transformation data didn’t perform well, so original data was applied. The first plot is a time series plot of the KRW/USD exchange spot. Plot shows when there is an economic crisis(ex.2009 financial crisis), KRW against USD increases significantly. 

The second plot shows the  returns of theKRW/USD exchange spot.  In this plot, volatility clustering is clearly observed: for most periods, the values are centered near zero, but in certain periods the series exhibits high volatility before returning to calmer behavior. This suggests that the data are potentially appropriate for modeling with the ARCH/GARCH family of models.




# ACF & PACF plot

::: panel-tabset


### ACF & PACF plot for  return of KRW/USD exchange spot(original,absolute value, squared)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)
kr_acf <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf/kr_pacf

```

From the plots, KOSPI Index data performs well in terms of autocorrelation by applying log transformation, However there are still some lag points showing autocorrelation. 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


ggAcf(abs(kr_return), lag.max = 30) +
  ggtitle("ACF plot of Absolute 
          KRW/USD exchange spot") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ggAcf(kr_return^2, lag.max = 30) +
  ggtitle("ACF plot of Squared
          KRW/USD exchange spot ") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```


### ARCH effect test

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

# Load required package
library(FinTS)

# Perform ARCH LM Test on Bitcoin returns
arch_test_result <- ArchTest(kr_return, lags = 1, demean = TRUE)

# Print results
print(arch_test_result)
```

p-vlaue is smaller than 0.05(default criterion), indicating rejecting null hypothesis, concluding strong evidence for the presence of ARCH(1) effects in the data.


:::

Two plots for applying absolute value and squaring to KRW/USD exchange spot shows significant autocorrelation throughout multiple lags, compare to log return. This implies that the returns are not independently and identically distributed, and gives evidence for need to apply conditional variance models such as ARCH or GARCH to capture the underlying time-varying volatility structure.

# Modeling 1: ARIMA +GARCH model

::: panel-tabset

### model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)

kr_acf <- ggAcf(kr_ts,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot ") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf <- ggPacf(kr_ts,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf/kr_pacf
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_acf_log <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf_log <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf_log/kr_pacf_log
```

ACF plot shows significant autocorrelation across lags. Also in the PACF plot, it has significant autocorrelation, then drops significantly, indicating almost no autocorrelation after lag1.these plots indicate the presence of dependencies between past and current price movements, series is stationary. 

ACF and PACF plot for KRW/USD exchange spot return shows that most of the lags are within threshold, however there are lags that spike, for example like lag4. For manual search, a search range from 0 to 4 seems appropriate. 

And both plots have similar patterns, indicating that conditional heteroskedasticity is present. So applying the ARCH/GARCH family model is appropriate. 

### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ARIMA.c <- function(p_min, p_max, q_min, q_max, data) {
  results <- matrix(NA, nrow = 0, ncol = 6)
  colnames(results) <- c("p", "d", "q", "AIC", "BIC", "AICc")

  for (p in p_min:p_max) {
    for (q in q_min:q_max) {
      for (d in 0:2) {
        if ((p + d + q) <= 12) {  # Complexity constraint
          fit <- Arima(data, order = c(p, d, q))
          metrics <- c(p, d, q, fit$aic, fit$bic, fit$aicc)
          results <- rbind(results, metrics)
        }
      }
    }
  }

  # Convert to data frame
  results_df <- as.data.frame(results)
  colnames(results_df) <- c("p", "d", "q", "AIC", "BIC", "AICc")
  return(results_df)
}

highlight_output = function(output, type="ARIMA") {
    highlight_row <- c(which.min(output$AIC), which.min(output$BIC), which.min(output$AICc))
    knitr::kable(output, align = 'c', caption = paste("Comparison of", type, "Models")) %>%
    kable_styling(full_width = FALSE, position = "center") %>%
    row_spec(highlight_row, bold = TRUE, background = "#FFFF99")  # Highlight row in yellow
}

output <- ARIMA.c(p_min = 0, p_max = 4, q_min = 0, q_max = 4, data = kr_ts)
highlight_output(output)

```

From the table, ARIMA(4,1,4) has lowest BIC,AIC and AICc

### auto.arima() model

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

auto_model2<-auto.arima(kr_ts)
auto_model2
```

### Model diagnostics 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_data<- kr_ts
kr_output1 <- capture.output(sarima(kr_data, 4, 1, 4))
start_line <- grep("Coefficients", kr_output1) 
end_line <- length(kr_output1)  
cat(kr_output1[start_line:end_line], sep = "\n")
```


From model diagnostic for three potential models, diagnostics are not satisfactory, to evaluate which model to choose, model AIC,BIC and coefficient's significance. In this sense, i would use ARIMA(4,1,4) model since it has lowest BIC value. Also auto.arima() suggested ARIMA(0,1,0)(0,0,1)[252], however as seen in EDA and univariate section, using ARIMA(4,1,4) is more appropriate. 


:::


# Residual fit

::: panel-tabset

### Residual ACF &PACF plot for KRW/USD exchange spot model(original & squared)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


arima_fit2 <- Arima(kr_ts, order = c(4,1,4), include.drift = TRUE)
res_arima2<- residuals(arima_fit2)

kr_res_acf <- ggAcf(res_arima2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_pacf <- ggPacf(res_arima2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_acf/kr_res_pacf

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_res_acf <- ggAcf(res_arima2^2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_pacf <- ggPacf(res_arima2^2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kr_res_acf/kr_res_pacf
```


From the ACF and PACF plots of the residuals and squared residuals for the ARIMA(4,1,4) model, the ACF of the squared residuals shows noticeable spikes up to lag 4, followed by a gradual decline. This suggests the presence of an ARCH effect, indicating time-varying volatility in the data. Based on these plots, an appropriate range for manual model search is p,q both in 0:4 range.


### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(tseries)
library(knitr)
library(kableExtra)

# Initialize list to store models and track p, q
models <- list()
pq_combinations <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

for (p in 0:4) {
  for (q in 0:4) {
    fit <- tryCatch(
      garch(res_arima2, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      pq_combinations <- rbind(
        pq_combinations,
        data.frame(p = p, q = q, AIC = AIC(fit))
      )
      cc <- cc + 1
    }
  }
}

# Round AIC for presentation
pq_combinations$AIC <- round(pq_combinations$AIC, 3)

# Identify row with minimum AIC
highlight_row <- which.min(pq_combinations$AIC)

# Create formatted table
pq_combinations %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")
```

From manual search, GARCH(2,1) model is better has lowest AIC

### Model selection 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(2,1):\n")
garch_model <- garchFit(~ garch(2, 1), data = res_arima2, trace = FALSE)
summary(garch_model)
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(1,1):\n")
garch_model <- garchFit(~ garch(1,1), data = res_arima2, trace = FALSE)
summary(garch_model)
```

By manual search to find optimal p,q value, GARCH(2,1) had lowest AIC. However when fitting a model with this parameter, alpha2 are not significant with large p value, trying other close by AIC values could be appropriate. After testing more model, all the coefficient for GARCH(1,1) model are significant and very close AIC value to lowest value, So further modeling GARCH(1,1) will be used. 

### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
#| 
arima_fit2 <- Arima(kr_ts, order = c(4,1,4), include.drift = TRUE)
arima_res2<-residuals(arima_fit2)
final.fit20<- garchFit(~ garch(1, 1), data = arima_res2, trace = FALSE)
summary(final.fit20)
garch_res30 <- residuals(final.fit20)
checkresiduals(garch_res30)
```


For final model, ARIMA(4,1,4)+GARCH(1,1) model was used. Model diagnostic give some intuition for this model. First residual plot shows it is good patterns, similar patterns with spikes. ACF plot also shows most lags fall into threshold, autocorrelation is resolved. however , for Ljung-Box test, it has very small p-value, indicating model fit is not satisfactory. However this model give all the coefficients as significant compare to other model choice, so this is the best model. 

### Forecast


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

fc <-predict(final.fit20, n.ahead = 100)
invisible(predict(final.fit20, n.ahead = 100, plot = TRUE))
```

:::

Equation: 

$$
(1 - \phi_1 B - \phi_2 B^2 - \phi_3 B^3 - \phi_4 B^4)(1 - B)x_t
= \delta + (1 + \theta_1 B + \theta_2 B^2 + \theta_3 B^3 + \theta_4 B^4)y_t,
$$


$$
\phi_1 = 0.2988,\quad
\phi_2 = 0.2035,\quad
\phi_3 = 0.3325,\quad
\phi_4 = -0.8808,
$$
$$
\theta_1 = -0.2817,\quad
\theta_2 = -0.1839,\quad
\theta_3 = -0.3645,\quad
\theta_4 = 0.7989,\quad
\delta = 0.0540.
$$


$$
\begin{aligned}
\Delta x_t
&= 0.0540
+ 0.2988\,\Delta x_{t-1}
+ 0.2035\,\Delta x_{t-2}
+ 0.3325\,\Delta x_{t-3} \\
&\quad - 0.8808\,\Delta x_{t-4}
+ y_t
- 0.2817\,y_{t-1}
- 0.1839\,y_{t-2} \\
&\quad - 0.3645\,y_{t-3}
+ 0.7989\,y_{t-4}.
\end{aligned}
$$

$$
y_t = \sigma_t \varepsilon_t,\qquad \varepsilon_t \sim \text{i.i.d. } N(0,1),
$$

$$
\sigma_t^2
= \omega + \alpha_1 y_{t-1}^2 + \beta_1 \sigma_{t-1}^2,
$$


$$
\omega = 0.114441,\quad
\alpha_1 = 0.061231,\quad
\beta_1 = 0.940516,
$$


$$
\sigma_t^2
= 0.114441
+ 0.061231\,y_{t-1}^2
+ 0.940516\,\sigma_{t-1}^2.
$$


# Modeling Approach 2: GARCH model

In the previous modeling, the overall model fit was not satisfactory. Therefore, in this section, a different modeling approach is used: directly applying models from the ARCH/GARCH family.

::: panel-tabset

### ACF & PACF plot of KRW/USD exchange spot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kr_acf_log <- ggAcf(kr_return,lag.max = 30)+ggtitle("ACF Plot of KRW/USD exchange spot") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kr_pacf_log <- ggPacf(kr_return,lag.max = 30)+ggtitle("PACF Plot of KRW/USD exchange spot") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kr_acf_log/kr_pacf_log

```

Based on the ACF and PACF plots, the parameter search range for the manual selection process will be set from 0 to 5 for both p and q.


### Manual Search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


# Initialize model storage
models <- list()
results <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Grid search for GARCH(p, q), where p = ARCH order, q = GARCH order
for (p in 1:5) {
  for (q in 1:5) {
    fit <- tryCatch(
      garch(kr_return, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      results <- rbind(results, data.frame(p = p, q = q, AIC = AIC(fit)))
      cc <- cc + 1
    }
  }
}

# Round AIC values for readability
results$AIC <- round(results$AIC, 3)

# Identify the model with the lowest AIC
highlight_row <- which.min(results$AIC)

# Display formatted table
results %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")

```


### Model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model2 <- garchFit(~ garch(1,3), data = kr_return, trace = FALSE)
summary(garch_model2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model3 <- garchFit(~ garch(1,1), data = kr_return, trace = FALSE)
summary(garch_model3)
```

The optimal model based on AIC is the GARCH(1,3) model. When testing the model with the lowest AIC, the overall fit was strong; however, not all coefficients were statistically significant, with some showing large p-values. Therefore,  additional model were considered:  GARCH(1,1).Comparing the two models, all coefficients in the GARCH(1,1) model were significant, so this model is selected as the final choice.


### Final Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch.fit2 <- garch(kr_return, order = c(1,1), trace = FALSE) 
summary(garch.fit2)

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_res2 <- residuals(garch.fit2)
checkresiduals(garch_res2)
```

From model diagnostics, this model shows similar result for ACF and residual plot compare to other model approach. However, for Ljung-Box test, it has much better p-value, indicating that this model has better model fit compare to other method. 

:::

Equation: 


$$
r_t = \sigma_t \varepsilon_t, \qquad \varepsilon_t \sim \text{i.i.d. } N(0,1),
$$


$$
\sigma_t^2 = \alpha_0 + \alpha_1 r_{t-1}^2 + \beta_1 \sigma_{t-1}^2.
$$


$$
\alpha_0 = 1.317\times 10^{-7}, \quad
\alpha_1 = 0.05447, \quad
\beta_1 = 0.9431,
$$


$$
\sigma_t^2
= 1.317\times 10^{-7}
+ 0.05447\, r_{t-1}^2
+ 0.9431\, \sigma_{t-1}^2.
$$


# Forecasting plot(365days): KRW/USD exchange spot 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
library(lubridate)
library(dplyr)
library(plotly)


gfit <- garchFit(~ garch(1,1),
                 data = as.numeric(kr_return),
                 trace = FALSE)

# Forecast 365 days
h <- 365
pf <- predict(gfit, n.ahead = h)
rhat <- as.numeric(pf$meanForecast)

# Convert differences to prices (simple addition)
last_price <- tail(as.numeric(kr$krw), 1)
price_fc <- numeric(h)
price_fc[1] <- last_price + rhat[1]
for (i in 2:h) {
  price_fc[i] <- price_fc[i-1] + rhat[i]
}

# Create future dates
last_date <- tail(kr$Date, 1) 
future_dates <- seq(last_date + 1, by = "day", length.out = h)

# Historical data
hist_df <- data.frame(
  Date = kr$Date,  
  Price = as.numeric(kr$krw)
)

# Forecast data
fc_df <- data.frame(Date = future_dates, Price = price_fc)

# Show recent 10 years
recent_window <- 3650
hist_df_recent <- tail(hist_df, recent_window)

# Plot
plot_ly() %>%
  add_lines(data = hist_df_recent, x = ~Date, y = ~Price, 
            name = "Historical", line = list(color="blue", width=2)) %>%
  add_lines(data = fc_df, x = ~Date, y = ~Price, 
            name = "GARCH Forecast", 
            line = list(color="red", dash="dash", width=3)) %>%
  layout(title = "KRW/USD Exchange Rate — GARCH(1,1) 365-Day Forecast",
         xaxis = list(title = "Date"),
         yaxis = list(title = "KRW per USD"),
         hovermode = "x unified")
```

# Volatility plot : KRW/USD exchange spot 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
set.seed(1)


garch.fit11 <- garchFit(~ garch(1,1), data = kr_return, trace = FALSE)
ht <- garch.fit11@h.t


data2 <- data.frame(Date = kr$Date[-1][1:length(ht)], Volatility = ht)



p <- ggplot(data2, aes(x = Date, y = Volatility)) +
  geom_line(color = 'orange') +
  labs(
    title = "Conditional Variance from GARCH(1,1) Model",
    x = "Date",
    y = "Conditional Variance"
  ) +
  theme_minimal()
ggplotly(p)
```









