---
title: "Financial Time Series Models(ARCH/GARCH)"
format: html
---

# Finance time series model(KOSPI,S&P500,krw/usd)

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
library(tidyverse)
library(ggplot2)
library(forecast)
library(astsa) 
library(xts)
library(zoo)
library(tseries)
library(fpp2)
library(fma)
library(lubridate)
library(tidyverse)
library(TSstudio)
library(tidyquant)
library(plotly)
library(readr)
library(kableExtra)
library(knitr)
library(patchwork)
library(vars)
library(here)
library(tsibble)
library(dplyr)
# calling data

#KR base rate
bok<- read.csv("../data/interest/bok.csv")%>%
  rename(Date = date)
bok$Date<- as.Date(bok$Date)
bok <- bok %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")


# FED rate 

usr<- read.csv("../data/interest/us_rate.csv")%>%
  rename(Date = observation_date,rate = DFF)
usr$Date<- as.Date(usr$Date)
usr<- usr %>%
  mutate(Date = floor_date(Date, unit = "quarter")) %>%
  group_by(Date) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")

# KRW/USD rate

kr <- read.csv("../data/fx rate/kor.csv")
kr <- kr %>%
  transmute(
    Date = as.Date(observation_date),
    krw  = DEXKOUS,    
    usd  = 1 / DEXKOUS  
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  complete(Date = seq(min(Date), max(Date), by = "day")) %>%

  fill(krw, usd, .direction = "down")


# USD index 

usd <- read_csv("../data/fx rate/usd_index.csv", show_col_types = FALSE)
usd <- usd %>%
  transmute(
    Date = as.Date(Date),
    usd_index = Close
  ) %>%
  filter(!is.na(Date)) %>%
  arrange(Date) %>%
  distinct(Date, .keep_all = TRUE) %>%
  complete(Date = seq(min(Date), max(Date), by = "day")) %>%
  fill(usd_index, .direction = "down")


# Yield data 

us_yield  <- read.csv(here("data/yield", "us_yield.csv"))
kor_yield   <- read.csv(here("data/yield", "kor_yield.csv"))


us_yield$Date  <- as.Date(us_yield$Date)
kor_yield$Date <- as.Date(kor_yield$Date)

colnames(us_yield)[colnames(us_yield)  == "X3Y"]  <- "US_3Y"
colnames(us_yield)[colnames(us_yield)  == "X10Y"] <- "US_10Y"
colnames(kor_yield)[colnames(kor_yield) == "X3Y"]  <- "KR_3Y"
colnames(kor_yield)[colnames(kor_yield) == "X10Y"] <- "KR_10Y"

us_yield  <- us_yield[,  c("Date", "US_3Y", "US_10Y")]
kor_yield <- kor_yield[, c("Date", "KR_3Y", "KR_10Y")]

us_yield  <- us_yield  %>% arrange(Date) %>% fill(US_3Y, US_10Y, .direction = "down")
kor_yield <- kor_yield %>% arrange(Date) %>% fill(KR_3Y, KR_10Y, .direction = "down")


df <- merge(us_yield, kor_yield, by = "Date")

df$US_3m10  <- df$US_3Y - df$US_10Y
df$KR_3m10  <- df$KR_3Y - df$KR_10Y
df$US_KR_3Y <- df$US_3Y - df$KR_3Y
df$US_KR_10Y<- df$US_10Y - df$KR_10Y


# S&P500 data
sp500 <- read_csv("../data/stock/sp500.csv")


# KOSPI data
kospi <- read_csv("../data/stock/kospi.csv")
kospi$Date <- as.Date(kospi$Date)

# VIX data(added for the modeling)
vix<- read_csv("../data/stock/vix.csv")%>%
  mutate(Date = ymd(Date)) %>%
  arrange(Date) %>%
  fill(vix, .direction = "down")


# extract spreads from df

us_spreads <- df %>%
  dplyr::select(Date, US_3m10) %>%
  rename(us_spread = US_3m10) %>%
  mutate(Date = as.Date(Date))

kor_spreads <- df %>%
  dplyr::select(Date, KR_3m10) %>%
  rename(kr_spread = KR_3m10) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_3y <- df %>%
  dplyr::select(Date, US_KR_3Y) %>%
  mutate(Date = as.Date(Date))

us_kr_spreads_10y <- df %>%
  dplyr::select(Date, US_KR_10Y) %>%
  mutate(Date = as.Date(Date))


```


# Time series plot

::: panel-tabset 


### candelstick plot for KOSPI Index 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

sp_plot <- plot_ly(
  data = kospi,
  x = ~Date,
  type = "candlestick",
  open = ~Open,
  high = ~High,
  low = ~Low,
  close = ~Close,
  name = "KOSPI Index"
) %>%
  layout(
    title = "KOSPI Index",
    yaxis = list(title = "KOSPI index"),
    xaxis = list(
      title = "Date",
      tickformat = "%Y",
      dtick = "M12"
    ),
    legend = list(x = 0.1, y = 0.9)
  )

sp_plot
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_close<- kospi$Close
kospi_ts <- ts(kospi_close,
          start = decimal_date(as.Date("1996-12-11")),
          frequency = 252)

kospi_return<- diff(log(kospi_ts))

autoplot(kospi_return) +
  ggtitle("Daily Log Returns of KOSPI Index") +
  xlab("Time") +
  ylab("Log Return")
```

:::


# ACF & PACF plot

::: panel-tabset


### ACF & PACF plot for log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)
kospi_acf <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf

```

From the plots, KOSPI Index data performs well in terms of autocorrelation by applying log transformation, However there are still some lag points showing autocorrelation. 


### ACF & PACF plot for log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


ggAcf(abs(kospi_return), lag.max = 30) +
  ggtitle("ACF plot of Absolute KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

### ACF & PACF plot for log return of KOSPI Index

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ggAcf(kospi_return^2, lag.max = 30) +
  ggtitle("ACF plot of Squared KOSPI Index Returns") +
  xlab("Lag") +
  ylab("Autocorrelation") +
  theme_minimal()
```

:::

Two plots for applying absolute value and squaring to KOSPI Index shows significant autocorrelation throughout multiple lags, compare to log return. This implies that the returns are not independently and identically distributed, and gives evidence for need to apply conditional variance models such as ARCH or GARCH to capture the underlying time-varying volatility structure.

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

# Load required package
library(FinTS)

# Perform ARCH LM Test on Bitcoin returns
arch_test_result <- ArchTest(kospi_return, lags = 1, demean = TRUE)

# Print results
print(arch_test_result)
```


# Modeling 1: ARIMA +GARCH model

::: panel-tabset

### model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(patchwork)

kospi_acf <- ggAcf(kospi_ts,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf <- ggPacf(kospi_ts,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf/kospi_pacf
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log
```

### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

ARIMA.c <- function(p_min, p_max, q_min, q_max, data) {
  results <- matrix(NA, nrow = 0, ncol = 6)
  colnames(results) <- c("p", "d", "q", "AIC", "BIC", "AICc")

  for (p in p_min:p_max) {
    for (q in q_min:q_max) {
      for (d in 0:2) {
        if ((p + d + q) <= 12) {  # Complexity constraint
          fit <- Arima(data, order = c(p, d, q))
          metrics <- c(p, d, q, fit$aic, fit$bic, fit$aicc)
          results <- rbind(results, metrics)
        }
      }
    }
  }

  # Convert to data frame
  results_df <- as.data.frame(results)
  colnames(results_df) <- c("p", "d", "q", "AIC", "BIC", "AICc")
  return(results_df)
}

highlight_output = function(output, type="ARIMA") {
    highlight_row <- c(which.min(output$AIC), which.min(output$BIC), which.min(output$AICc))
    knitr::kable(output, align = 'c', caption = paste("Comparison of", type, "Models")) %>%
    kable_styling(full_width = FALSE, position = "center") %>%
    row_spec(highlight_row, bold = TRUE, background = "#FFFF99")  # Highlight row in yellow
}

output <- ARIMA.c(p_min = 0, p_max = 5, q_min = 0, q_max = 5, data = log(kospi_ts))
highlight_output(output)

```

From the table, arima(0,1,1) has lowest BIC and arima(5,1,5) has lowest AIC and AICc
### auto.arima() model

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

auto_model1<-auto.arima(log(kospi_ts))
auto_model1
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_data<-log(kospi_ts)
kospi_output1 <- capture.output(sarima(kospi_data, 0, 1, 1))
start_line <- grep("Coefficients", kospi_output1) 
end_line <- length(kospi_output1)  
cat(kospi_output1[start_line:end_line], sep = "\n")
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output2 <- capture.output(sarima(kospi_data, 5, 1, 5))
start_line <- grep("Coefficients", kospi_output2) 
end_line <- length(kospi_output2)  
cat(kospi_output2[start_line:end_line], sep = "\n")

```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_output3 <- capture.output(sarima(kospi_data, 2, 1, 2))
start_line <- grep("Coefficients", kospi_output3) 
end_line <- length(kospi_output3)  
cat(kospi_output3[start_line:end_line], sep = "\n")
```

From model diagnostic for three potential models, diagnostics are not satisfactory, to evaluate which model to choose, model AIC,BIC and coefficient's significance. In this sense, i would use ARIMA(0,1,1) model since it has lowest BIC value. 


:::


# residual fit


::: panel-tabset

### Residual ACF &PACF plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf

```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
res_arima1<- residuals(arima_fit1)

kospi_res_acf <- ggAcf(res_arima1^2,lag.max = 30)+ggtitle("ACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_pacf <- ggPacf(res_arima1^2,lag.max = 30)+ggtitle("PACF Plot of ARIMA(0,1,1) Residuals") 

kospi_res_acf/kospi_res_pacf
```



### Manual search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(tseries)
library(knitr)
library(kableExtra)

# Initialize list to store models and track p, q
models <- list()
pq_combinations <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Fit GARCH(p, q) models for p = 1:7 and q = 1:7
for (p in 0:5) {
  for (q in 0:5) {
    fit <- tryCatch(
      garch(res_arima1, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      pq_combinations <- rbind(
        pq_combinations,
        data.frame(p = p, q = q, AIC = AIC(fit))
      )
      cc <- cc + 1
    }
  }
}

# Round AIC for presentation
pq_combinations$AIC <- round(pq_combinations$AIC, 3)

# Identify row with minimum AIC
highlight_row <- which.min(pq_combinations$AIC)

# Create formatted table
pq_combinations %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(2,3):\n")
garch_model <- garchFit(~ garch(2, 3), data = res_arima1, trace = FALSE)
summary(garch_model)
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
cat("\nSummary for GARCH(2,1):\n")
garch_model <- garchFit(~ garch(2, 1), data = res_arima1, trace = FALSE)
summary(garch_model)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

cat("\nSummary for GARCH(1,1):\n")
garch_model <- garchFit(~ garch(1,1), data = res_arima1, trace = FALSE)
summary(garch_model)
```
By manual search to find optimal p,q value, GARCH(2,3) had lowest AIC. However when fitting a model with this parameter, beta 1 and beta 2 are not significant with large p value, trying other close by AIC values could be appropriate. After testing two more models, all the coefficient for GARCH(1,1) model are significant and very close AIC value to lowest value, So further modeling GARCH(1,1) will be used. 

### Final model 

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true
#| 
arima_fit1 <- Arima(log(kospi_ts), order = c(0,1,1), include.drift = TRUE)
arima_res1<-residuals(arima_fit1)
final.fit1<- garchFit(~ garch(1, 1), data = arima_res1, trace = FALSE)
summary(final.fit1)
```
### forecasting
```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

fc <-predict(final.fit1, n.ahead = 100)
invisible(predict(final.fit1, n.ahead = 100, plot = TRUE))
```

:::


# Modeling Approach 2: GARCH model

::: panel-tabset

# ACF & PACF plot

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

kospi_acf_log <- ggAcf(kospi_return,lag.max = 30)+ggtitle("ACF Plot of KOSPI Index") + theme_bw() +
  geom_segment(lineend = "butt", color = "orange") +
    geom_hline(yintercept = 0, color = "orange") 
kospi_pacf_log <- ggPacf(kospi_return,lag.max = 30)+ggtitle("PACF Plot of KOSPI Index") + theme_bw()+
  geom_segment(lineend = "butt", color = "skyblue") +
    geom_hline(yintercept = 0, color = "skyblue") 

kospi_acf_log/kospi_pacf_log

```

### Manual Search

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


# Initialize model storage
models <- list()
results <- data.frame(p = integer(), q = integer(), AIC = numeric())
cc <- 1

# Grid search for GARCH(p, q), where p = ARCH order, q = GARCH order
for (p in 1:5) {
  for (q in 1:5) {
    fit <- tryCatch(
      garch(kospi_return, order = c(q, p), trace = FALSE),
      error = function(e) NULL
    )
    if (!is.null(fit)) {
      models[[cc]] <- fit
      results <- rbind(results, data.frame(p = p, q = q, AIC = AIC(fit)))
      cc <- cc + 1
    }
  }
}

# Round AIC values for readability
results$AIC <- round(results$AIC, 3)

# Identify the model with the lowest AIC
highlight_row <- which.min(results$AIC)

# Display formatted table
results %>%
  kable(
    caption = "AIC Comparison for GARCH(p, q) Models",
    col.names = c("ARCH Order (p)", "GARCH Order (q)", "AIC"),
    align = c("c", "c", "c"),
    booktabs = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  ) %>%
  row_spec(highlight_row, bold = TRUE, background = "#FFF59D")

```


### Model selection

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model1 <- garchFit(~ garch(4,3), data = kospi_return, trace = FALSE)
summary(garch_model1)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model2 <- garchFit(~ garch(2,1), data = kospi_return, trace = FALSE)
summary(garch_model2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_model3 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
summary(garch_model3)
```

### Model fit

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


garch.fit2 <- garch(kospi_return, order = c(1,1), trace = FALSE) 
summary(garch.fit2)
```


```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

garch_res1 <- residuals(garch.fit2)
checkresiduals(garch_res1)
```

### forecasting

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true


library(fGarch)
library(lubridate)
library(dplyr)
library(plotly)


gfit <- garchFit(~ garch(1,1),
                 data = as.numeric(kospi_return),
                 trace = FALSE)

h <- 365
pf <- predict(gfit, n.ahead = h)
rhat <- as.numeric(pf$meanForecast)


last_price <- tail(as.numeric(kospi_close), 1)
price_fc <- numeric(h)
price_fc[1] <- last_price * exp(rhat[1])
for (i in 2:h) {
  price_fc[i] <- price_fc[i-1] * exp(rhat[i])
}

last_date <- tail(kospi$Date, 1) 
future_dates <- seq(last_date + 1, by = "day", length.out = h)

hist_df <- data.frame(
  Date = kospi$Date,  
  Price = as.numeric(kospi_close)
)

fc_df <- data.frame(Date = future_dates, Price = price_fc)

recent_window <- 3650 # recent 10 years
hist_df_recent <- tail(hist_df, recent_window)

plot_ly() %>%
  add_lines(data = hist_df_recent, x = ~Date, y = ~Price, 
            name = "Historical", line = list(color="blue")) %>%
  add_lines(data = fc_df, x = ~Date, y = ~Price, 
            name = "GARCH Forecast", 
            line = list(color="red", dash="dash")) %>%
  layout(title = "KOSPI — GARCH(1,1) 365-Day Price Forecast",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Index"),
         hovermode = "x unified")
```

```{r,warning=FALSE,message=FALSE}
#| echo: true
#| code-fold: true

library(fGarch)
set.seed(1)

garch.fit11 <- garchFit(~ garch(1,1), data = kospi_return, trace = FALSE)
ht <- garch.fit11@h.t


data2 <- data.frame(Date = kospi$Date[-1][1:length(ht)], Volatility = ht)



p <- ggplot(data2, aes(x = Date, y = Volatility)) +
  geom_line(color = 'orange') +
  labs(
    title = "Conditional Variance from GARCH(1,1) Model",
    x = "Date",
    y = "Conditional Variance"
  ) +
  theme_minimal()

# Convert to plotly
ggplotly(p)
```















